### 2021-11-30 plos_latex_template.tex
RJ: Edits to rule 3

A genuinely inclusive conference can only be organized by an inclusive and diverse organizing team in charge of the conference decision-making.
Organizers should be a team with people from different regions, genders, races and ethnicities, socioeconomic statuses, and other aspects of diversity.
Having diverse people in decision-making positions will positively affect all the other aspects of your conference because all the processes will benefit from their input, expertise, and distinct perspectives \cite{hongGroupsDiverseProblem2004}. 
In addition, a diverse team plays an important role in creating a welcoming space because representation--seeing people with similar life experiences occupy public spaces, positions of power, and breaking negative stereotypes--is one of the best ways to create a sense of belonging for everyone participating in the conference (see Rule 2 about a safe and welcoming environment). If you already started assembling an organizing team, check for gaps in its composition. 
The regional and local communities, groups, or associations in your field are good sources to tap into.

% Rocío: Idea of this paragraph: non-transferability and do not restrict people
People with disabilities often say: `Nothing about us without us'; the same holds for other dimensions of diversity. This means that the actual life experiences, expertise, and insights from people in marginalized groups cannot be replaced by good intentions from people outside these groups \cite{costanzachockDesign2020}.
People who have experienced exclusion have the social and technical expertise to fight against it and they will be essential in any team.%ast maybe frame this on a more positive note (ideas, problem solving)
However, they must have the freedom to choose in which areas of the conference they want to work and not be restricted to diversity and inclusion aspects. 
% Rocío: Idea of this paragraph: tips to make a diverse and inclusive team work + paying them
When working with people from marginalized groups do not assume that self-nomination and voting will work as mechanisms to choose leadership positions. Instead, nominate directly and offer leading positions that would normally be occupied by people from privileged groups.
Build an environment in which every person can express their opinion and pay special attention to people from systematically excluded groups.
Many people lack the institutional support to put time and effort into the organization tasks and do not have the luxury to commit to the organization for free; consider paying them as an item in your budget.  
% Rocío: Add other types of recognition besides money (website, public recognition on social media, during the conference, etc.)
In addition, tasks such as receiving and responding to Code of Conduct reports can be emotionally intense work and should be additionally rewarded.

>>>>

A genuinely inclusive conference can only be organized by an inclusive and diverse organizing team in charge of the conference decision-making.
Organizers should be a team with people from different regions, genders, ethnicities, socioeconomic statuses, and other aspects of diversity.
Having diverse people in decision-making positions will positively affect all the other aspects of your conference because all the processes will benefit from their input, expertise, and distinct perspectives \cite{hongGroupsDiverseProblem2004}. 
In addition, a diverse team plays an important role in creating a welcoming space because representation--seeing people with similar life experiences occupy public spaces, positions of power, and breaking negative stereotypes--is one of the best ways to create a sense of belonging for everyone participating in the conference (see Rule 2 about a safe and welcoming environment). If you already started assembling an organizing team, check for gaps in its composition. 
The regional and local communities, groups, or associations in your field are good sources to tap into.

% Rocío: Idea of this paragraph: non-transferability and do not restrict people
People with disabilities often say: `Nothing about us without us'; the same holds for other dimensions of diversity. The experience of people in marginalized groups facing barriers for equal participation and trying to solve them are invaluable; they cannot be replaced by good intentions from people that have not been through the same experiences \cite{costanzachockDesign2020}.
% People who have experienced exclusion have the social and technical expertise to fight against it and they will be essential in any team.%ast maybe frame this on a more positive note (ideas, problem solving)
However, do not require nor expect minoritized people to only work—or want to work—on diversity and inclusion aspects; 
everybody must have the freedom to choose in which areas of the conference they want to work. 
% Rocío: Idea of this paragraph: tips to make a diverse and inclusive team work + paying them
Furthermore, do not assume that self-nomination and voting will work as mechanisms to choose leadership positions. Instead, nominate directly and offer leading positions that would normally be occupied by people from privileged groups.
Build an environment in which every person can express their opinion and pay special attention to people from systematically excluded groups.
Many people lack the institutional support to put time and effort into the organization tasks and do not have the luxury to commit to the organization for free; consider paying them as an item in your budget as well as other types of recognition (e.g. public recognition on social media, on the conference website, or during the conference).
In addition, tasks such as receiving and responding to Code of Conduct reports can be emotionally intense work and should be additionally rewarded.
